BigArchive: Low-cost and Scalable Deduplication Storage for VM Snapshot

### 2012-12-20 snapshot_system/delete.tex
paper update

\subsection{Challenges}
Contrary to a traditional backup system, a dedupe system shares data among files by default. 
Reference management is necessary to keep track of chunk usage and reclaim freed space. 
In addition to scalability and speed, reliability is another challenge for reference management. 
If a chunk gets freed while it is still referenced by snapshots, data loss occurs and files cannot be restored. 
On the other hand, if a chunk is referenced when it is actually no longer in use, it causes storage leakage.

Reference counting, while being simple, suffers from low reliability especially in our distributed environment, 
because it is vulnerable to lost or repeated updates: when errors occur some chunks maybe updated and some may not. 
Complicated transaction rollback logic is required to make reference counts consistent. Moreover, 
there is almost no way to verify if the reference count is correct or not in a large dynamic system. 
In real deployments, where data integrity and recoverability directly affect product reputation, simple reference counting is unsatisfactory.

Mark-and-sweep is generally a better solution. During the mark phase, all snapshot recipes are traversed so as to mark the used chunks. 
In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
This approach is very resilient to errors: at any time the process can simply be restarted with no negative side effects. 
Scalability, however, is an issue. {\em needs to explain its resource usage}

@@

\subsection{Fuzzy Deletion}
We design fuzzy deletion to fast identify unused data in the append store.
Instead of scanning the whold append store, it uses a bloom filter to check 
if a data are still referenced by living snapshots. However, there is a small false-positive probility which
would indetify unused data as in use, i.e., storage leakage.
The following steps would take place during an fuzzy deletion:

The overall time of running a fuzzy deletion for one snapshot deletion would be scanning
all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
parallel and is much faster than loading recipes from DFS:
\begin{equation}
T = (N_{SS} + 1) * T_{scan\_recipes}
\end{equation}

Using the example and analysis in previous section, this fuzzy deletion can be done in 5 minutes. 
Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
when set $P_{bl}$ to 0.01, the memory footprint of fuzzy deletion is about 15 MB.

The design goal of fuzzy deletion is to reduce the frequency of running accurate deletion.
For one VM's snapshots, let $D_{leakage}$ be the amount of storage leakage, $D_{del}$ be the average amount of data
to be deleted in one snapshot deletion, 
then we have:
\begin{equation}
D_{leakage} = N_{fuzzy} * P_{bl} * D_{del}
\end{equation}
where $N_{fuzzy}$ is the number of runs of fuzzy deletion. 
An accurate deletion is triggered to fix the storage leakage
when $D_{leakage}/D_{del}$ is accmulated to exceed certain threshold $T$:
\begin{equation}
D_{leakage} / D_{del} = N_{fuzzy} * P_{bl} > T \Rightarrow N_{fuzzy} > T/P_{bl}
\end{equation}
Therefore, when $P_{bl} = 0.01$ and $T=1$, 
there would be a run of accurate deletion for every $T/P_{bl} = 100$ runs of fuzzy deletion.
On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
one accurate deletion scheduled per day.

>>>>

% \subsection{Challenges}
% Contrary to a traditional backup system, a dedupe system shares data among files by default. 
% Reference management is necessary to keep track of chunk usage and reclaim freed space. 
% In addition to scalability and speed, reliability is another challenge for reference management. 
% If a chunk gets freed while it is still referenced by snapshots, data loss occurs and files cannot be restored. 
% On the other hand, if a chunk is referenced when it is actually no longer in use, it causes storage leakage.

% Reference counting, while being simple, suffers from low reliability especially in our distributed environment, 
% because it is vulnerable to lost or repeated updates: when errors occur some chunks maybe updated and some may not. 
% Complicated transaction rollback logic is required to make reference counts consistent. Moreover, 
% there is almost no way to verify if the reference count is correct or not in a large dynamic system. 
% In real deployments, where data integrity and recoverability directly affect product reputation, simple reference counting is unsatisfactory.

% Mark-and-sweep is generally a better solution. During the mark phase, all snapshot recipes are traversed so as to mark the used chunks. 
% In the sweep phase all chunks are swept and unmarked chunks are reclaimed. 
% This approach is very resilient to errors: at any time the process can simply be restarted with no negative side effects. 
% Scalability, however, is an issue. {\em needs to explain its resource usage}

\subsection{Approximate Deletion}
We design approximate deletion to fast identify unused data in the append store.
Instead of scanning the whold append store, it uses a bloom filter to check 
if a data are still referenced by living snapshots. However, there is a small false-positive probility which
would indetify unused data as in use, i.e., storage leakage.
The following steps would take place during an approximate deletion:

The overall time of running a approximate deletion for one snapshot deletion would be scanning
all the living snapshots and deleted snapshots, since operations on the in-memory bloom filter can be done in
parallel and is much faster than loading recipes from DFS:
\begin{equation}
T = (N_{SS} + 1) * T_{scan\_recipes}
\end{equation}

Using the example and analysis in previous section, this approximate deletion can be done in 5 minutes. 
Memory usage of the bloom filter depends on its false-positive probility $P_{bl}$,
when set $P_{bl}$ to 0.01, the memory footprint of approximate deletion is about 15 MB.

The design goal of approximate deletion is to reduce the frequency of running accurate deletion.
For one VM's snapshots, let $D_{leakage}$ be the amount of storage leakage, $D_{del}$ be the average amount of data
to be deleted in one snapshot deletion, 
then we have:
\begin{equation}
D_{leakage} = N_{approximate} * P_{bl} * D_{del}
\end{equation}
where $N_{approximate}$ is the number of runs of approximate deletion. 
An accurate deletion is triggered to fix the storage leakage
when $D_{leakage}/D_{del}$ is accmulated to exceed certain threshold $T$:
\begin{equation}
D_{leakage} / D_{del} = N_{approximate} * P_{bl} > T \Rightarrow N_{approximate} > T/P_{bl}
\end{equation}
Therefore, when $P_{bl} = 0.01$ and $T=1$, 
there would be a run of accurate deletion for every $T/P_{bl} = 100$ runs of approximate deletion.
On a machine that hosts 20 VMs and each VM deletes snapshot daily, there would be less than
one accurate deletion scheduled per day.

@@

### 2012-12-20 snapshot_system/design1.tex
paper update

\section{Multi-level Snapshot Deduplication}
\label{sect:dedupe}

\subsection{Snapshot System}
%system arch
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China. 
A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of xen-based\cite{Barham2003} VMs.

Aliyun has built a hadoop-like platform, which includes
several highly scalable cloud infrastructure services to support
 runing large scale VM cloud service:
\begin{itemize}
\item \textbf{DFS}: a distributed file system that is optimized for many large and sequential reads or appends.
\item \textbf{KV}: a distributed key-value store for managing structured data.
\item \textbf{MP}: a distributed data processing framework which is similar to Map-Reduce\cite{Dean2004}.
\item \textbf{MemCache}: a distributed memory object caching system.
\end{itemize}
%GFS-like\cite{googlefs03} 
%BigTable-like\cite{Chang2008a} 
Our snapshot system and the virtual machine management service rely on these basic cloud services
to be functional:
DFS holds the responsibility of managing physical disk storage
in the cloud, all data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
In addition, our snapshot system 
places the index of CDS in MemCache for deduplication, 
stores small amount of snapshot metadata in KV, and uses FX to facilitate the offline
data processing. All the above services can easily find their open-source counterparts,
which shows the generality of our architecture and deduplication scheme.

@@

%snapshot representation
\subsection{Snapshot Representation}
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break 
segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

\begin{figure}[htbp]
  \centering
  \epsfig{file=images/snapshot_representation.eps, width=3.7in}
  \caption{An example of snapshot representation.}
  \label{fig:snapshot}
\end{figure}
As a result, the representation of each snapshot is designed as a two-level index data structure 
in the form of a hierarchical directed acyclic graph as shown in Figure \ref{fig:snapshot}.
A snapshot recipe contains a list of segments, each of which is represented as a segment recipe
that holds the meatdata of its chunks. We choose this two-level structure because in practice we
observe that during each backup period only a small amount of VM data are added or modified. 
As the result, even the metadata of two snapshots can be highly similar, 
thus aggregating a large number of chunks as one segment can significantly reduce the space cost of snapshot metadata.
Furthermore, instead of using variables-sized segments, we use a dirty bit to capture the change status of fix-sized
segments which greatly ease the segment-level deduplication.

In both two kind of recipes, 
they do not include the actual data but only have
 references point to the data which are either stored in append store or CDS.
In our implementation the data reference is a 8 bytes field which is either an 
ASID (discuss in \ref{sect:append} or an offset of 
An additional flag indicates

\subsection{Multi-level Deduplication}
The multi-level deduplication scheme is designed base on the observations on the VM snapshot data from production cloud.
We found snapshot data duplication can be easily classified into two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize the cost of deduplication while maximize the its efficiency at each level,
and it is highly parallelizable since each segment is processed independently.

\subsubsection{Inner-VM Deduplication}
\label{sect:InnerVM}
The first-level deduplication is logically localized within each VM.
Such localization increases data independency between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.

The inner VM deduplication contains two levels of duplicate detection efforts:
\begin{itemize}
\item \textit{Level 1 Segment modification detection}.
If a segment is not changed, then its segment recipe can be simply reused by copying the data
reference from previous snapshot recipe. 
\item \textit{Level 2  Chunk fingerprint comparison.}
If a segment is modified, we perform fine-grained deduplication 
by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
thus eliminate partial data duplication within the segment.
\end{itemize}

In general, operations at level 1 have almost no cost and most of unmodified data are filtered here. 
To process a dirty segment at level 2, 
there requires no more than one DFS access to load the segment recipe from previous snapshot,
and a tiny amount of memory to hold it in main memory.
\textit{may need details here}

\subsubsection{Cross-VM Deduplication}
\label{sect:CrossVM}

\subsection{Common Data Set}
%arch
%analysis

>>>>

\section{Prototype Design}
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China. 
A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of xen-based\cite{Barham2003} VMs.

Aliyun has built a hadoop-like platform, which includes
several highly scalable cloud infrastructure services to support
 runing large scale VM cloud service:
\begin{itemize}
\item \textbf{DFS}: a distributed file system that is optimized for many large and sequential reads or appends.
%\item \textbf{KV}: a distributed key-value store for managing structured data.
\item \textbf{MapReduce}: a distributed data processing framework supports Map-Reduce\cite{Dean2004}.
\item \textbf{MemCache}: a distributed memory object caching system.
\end{itemize}
Our snapshot system and the virtual machine management service rely on these basic cloud services
to be functional:
DFS holds the responsibility of managing physical disk storage
in the cloud, all data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
In addition, our snapshot system 
places the index of CDS in MemCache for deduplication, 
and uses MapReduce to facilitate the offline
data processing. All the above services can easily find their open-source counterparts,
which shows the generality of our architecture and deduplication scheme.

@@

\input{snapshot}
\input{append}
\input{delete}

### 2012-12-20 snapshot_system/intro.tex
paper update

\section{Introduction}

%1.how virtual machines work on storage
%2.cow and why they are not good
%3.introduce dedup
%1

%Virtualization is the engine behind many popular cloud computing platforms.
%Amazon, Alibaba,  and many others have provided public VM clouds that host 
%tens of thousands of  virtual machines(VM) dynamically created
%for various active users. 
%In the  case of Alibaba cloud service, the sevice is called Aliyu, which
%provides the largest public cloud in based on the open-source Xen technology.
In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
each instance of a guest operating system runs on a virtual machine, accessing
virtual hard disks represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
Because these image files are stored as regular files from the external point of view,
backing up VM's data is mainly done by taking snapshots of virtual disk images.

A snapshot preserves the data of a VM's file system at a specific point in time. 
VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
%Even though the snapshots are saved incrementally, 
%when deleting a snapshot, only the data not needed for any other snapshot is removed. 
%So regardless of which prior snapshots have been deleted, all active snapshots will contain 
%all the information needed to restore the virtual disk.
%Snapshots can also be shared to instantiate multiple new virtual disks, such that user can make
%duplicate VMs with exact the same disk state. This feature is especially useful when a user wants to run
%an application on multiple VMs, for example Hadoop or MPI.

@@

%Restricting the scope of global deduplication reduces
%the inter-component  data dependenc during machine failure.

%Several operations are provided for creating and managing snapshots and snapshot trees,
%such as create snapshots, revert to any snapshot, and remove snapshots.
%VM snapshots is different from traditional file system backup from a few aspects:
%\begin{enumerate}
%\item The backup loads are heavy but resources are limited. The whole VM cluster have PBs of data and need to be backuped at daily basis, if not more frequently. But at the same time snapshot tasks must not affect the normal VM operations, which means only a tiny slice of CPU and memory can be used for this purpose.
%\item No file system semantics are provided. Snapshot operations are taken place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided.
%\item Snapshots can be shared between users. This does not only complicates the parent-child relationship between snapshots, but also require all snapshots be managed in a global namespace.
%\end{enumerate}

%In this paper we intorduce the deduplication scheme of snapshot storage in Aliyun's VM cloud. We exploit the 
The rest of the paper is arranged as follows. 
Section ~\ref{sect:background}
discusses on some background and related work.
Section~\ref{sect:options} discusses the requirements and  design options.
Section ~\ref{sect:arch} presents our snapshot backup architecture with multi-level selective deduplication 
Section ~\ref{sect:exper} presents  our evaluation results on the effectiveness
of multi-level deduplication for snapshot backup. 
Section ~\ref{sect:final} concludes this paper.
% talks about Aliyun's VM snapshot system and deduplication process. In section 4 we present
%the snapshot deduplication results of our real user VMs.

>>>>

\section{Introduction}
In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
each instance of a guest operating system runs on a virtual machine, accessing
virtual hard disks represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
Because these image files are stored as regular files from the external point of view,
backing up VM's data is mainly done by taking snapshots of virtual disk images.

A snapshot preserves the data of a VM's file system at a specific point in time. 
VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}.

@@

The following table shows the strength and weakness of some well-know deduplication systems:
\begin{table}
    \begin{tabular}{|l|l|l|l|}
        \hline
        ~           & Scalability & Low-cost & Full Dedup \\ \hline
        DDFS        & N           & N        & Y          \\ 
        Ex-bin      & Y           & Y        & N          \\ 
        Guo         & Y           & N        & N          \\ 
        iDedup      & N           & Y        & N          \\ 
        Founadation & N           & N        & Y          \\
        \hline
    \end{tabular}
\end{table}

### 2012-12-20 snapshot_system/snapshot.tex
paper update

\section{Multi-level Snapshot Deduplication}
\label{sect:dedupe}

\subsection{Snapshot System}
%system arch
Our architecture is built on the Aliyun platform which provides the largest public VM cloud in China. 
A typical VM cluster in our cloud environment
consists of from hundreds to thousands of physical machines, each of which can
host tens of xen-based\cite{Barham2003} VMs.

Aliyun has built a hadoop-like platform, which includes
several highly scalable cloud infrastructure services to support
 runing large scale VM cloud service:
\begin{itemize}
\item \textbf{DFS}: a distributed file system that is optimized for many large and sequential reads or appends.
\item \textbf{KV}: a distributed key-value store for managing structured data.
\item \textbf{MP}: a distributed data processing framework which is similar to Map-Reduce\cite{Dean2004}.
\item \textbf{MemCache}: a distributed memory object caching system.
\end{itemize}
%GFS-like\cite{googlefs03} 
%BigTable-like\cite{Chang2008a} 
Our snapshot system and the virtual machine management service rely on these basic cloud services
to be functional:
DFS holds the responsibility of managing physical disk storage
in the cloud, all data needed for VM services, such as virtual disk images used by runtime VMs,
and snapshot data for backup purposes, reside in this distributed file system. 
In addition, our snapshot system 
places the index of CDS in MemCache for deduplication, 
stores small amount of snapshot metadata in KV, and uses FX to facilitate the offline
data processing. All the above services can easily find their open-source counterparts,
which shows the generality of our architecture and deduplication scheme.

User control VMs through the virtual machine management service.
During VM creation, a user chooses a pre-configured VM image or
a snapshot that contains an OS,
then the VM management service 
copies the corresponding VM image to her VM as the OS disk.
Data disks can be created and mounted onto the VM in the same way,
either empty or from an existing snapshot. 
All these virtual disks are represented as virtual disk image files in our
underline runtime VM storage system.  
To avoid network latency and congestion, 
our distributed file system place the primary replica of VM's 
image files at physical machine of VM instance.
When user deletes her VM, all the runtime virtual disk images and
their snapshot data are removed from DFS.

%ss operations
In each VM, 
the runtime I/O between virtual machine and its virtual
disks is tunneled by the virtual device driver (called TapDisk\cite{Warfield2005} at Xen).
This is also where our snapshot system is built in. Three major snapshot operations are supported:
\begin{itemize}
\item \textit{Write snapshot}: save the current state of virtual disk as a snapshot.
This is also where data deduplication would take place.
During snapshot backup, concurrent disk write is logged 
to ensure a consistent snapshot version is captured. 
\item \textit{Read snapshot}: restore the state of virtual disk from a snapshot.
\item \textit{Delete snapshot}: delete a snapshot and reclaim the disk space for unused data.
\end{itemize}

\begin{figure}[htbp]
  \centering
  %\epsfig{file=images/arch.eps, height=2in, width=2.66in}
  \epsfig{file=images/arch.eps, width=3.9in}
  \caption{Snapshot backup architecture of each node.}
  \label{fig:arch}
\end{figure}

Figure~\ref{fig:arch} shows the architecture view of our snapshot service
at each node. The snapshot broker provides the functional interface for  snapshot backup, access, and deletion.
The inner-VM  deduplication is conducted by the broker to access meta data in the snapshot data store
and we discuss this in details in Section~\ref{sect:innerVM}.
The cross-VM deduplication is conducted by the broker to access 
a common data set (CDS) (will discuss in Section~\ref{sect:crossVM},
whose block hash index is stored in a distributed memory cache.

%snapshot representation
\subsection{Snapshot Representation}
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break 
segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

@@

\subsection{Multi-level Deduplication}
The multi-level deduplication scheme is designed base on the observations on the VM snapshot data from production cloud.
We found snapshot data duplication can be easily classified into two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize the cost of deduplication while maximize the its efficiency at each level,
and it is highly parallelizable since each segment is processed independently.

\subsubsection{Inner-VM Deduplication}
\label{sect:InnerVM}
The first-level deduplication is logically localized within each VM.
Such localization increases data independency between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.

The inner VM deduplication contains two levels of duplicate detection efforts:
\begin{itemize}
\item \textit{Level 1 Segment modification detection}.
If a segment is not changed, then its segment recipe can be simply reused by copying the data
reference from previous snapshot recipe. 
\item \textit{Level 2  Chunk fingerprint comparison.}
If a segment is modified, we perform fine-grained deduplication 
by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
thus eliminate partial data duplication within the segment.
\end{itemize}

@@

\subsubsection{Cross-VM Deduplication}
\label{sect:CrossVM}

\subsection{Common Data Set}
%arch
%analysis

>>>>

\subsection{Snapshot Deduplication}
\label{sect:dedupe}
%snapshot representation
\subsubsection{Snapshot Representation}
The virtual device driver uses a bitmap to track the changes 
that have been made to virtual disk.
Every bit in the bitmap represents a fix-sized (2MB) region called \textit{segment}, indicates whether the segment
is modified since last backup. Hence we could treat segment as the basic unit in snapshot backup similar to
file in normal backup: a snapshot could share a segment with previous snapshot it is not changed. 
Moreover, we break 
segments into var-sized chunks (average 4KB) using content-based chunking algorithm,
which brings the opportunity of fine-grained deduplication by
allowing data sharing between segments.

@@

\subsubsection{Multi-level Deduplication}
The multi-level deduplication scheme is designed base on the observations on the VM snapshot data from production cloud.
We found snapshot data duplication can be easily classified into two categories: \textit{Inner-VM} and \textit{Cross-VM}. 
Inner-VM duplication exists between VM's snapshots, because the majority of data are unchanged during each backup period. 
On the other hand, Cross-VM duplication is mainly due to widely-used software and libraries such as Linux and MySQL. 
As the result, different VMs tend to backup large amount of highly similar data.
Our multi-level pipeline process can minimize the cost of deduplication while maximize the its efficiency at each level,
and it is highly parallelizable since each segment is processed independently.

\textbf{Inner-VM Deduplication.}
The first-level deduplication is logically localized within each VM.
Such localization increases data independency between different VM backups,
simplifies snapshot management and statistics collection,
and facilitates parallel execution of snapshot operations.

Inner VM deduplication contains two levels of duplicate detection efforts:
\begin{itemize}
\item \textit{Level 1 Segment modification detection}.
If a segment is not changed, then its segment recipe can be simply reused by copying the data
reference from previous snapshot recipe. 
\item \textit{Level 2  Chunk fingerprint comparison.}
If a segment is modified, we perform fine-grained deduplication 
by comparing the fingerprints of its chunks to the same segment's recipe in the previous snapshot,
thus eliminate partial data duplication within the segment.
\end{itemize}

@@

\textbf{Cross-VM Deduplication.}

\subsection{Common Data Set}
